LHC abort gap monitor electronics upgrade

### 2024-04-21 paper.tex
rephrased introduction

\section{Introduction}
The LHC can store a maximum beam energy of up to 350 MJ across 2808 bunches
during its flat-top phase, with an average transverse beam size under 1 mm
(LHCreport). This high energy density poses a risk of machine damage, as
conductive surface intervention can melt metallic surfaces and quench
superconducting magnets. The Beam Dump system, utilizing kicker magnets with a
3-microsecond ramp-up time to diverting particles, takes care of removing the beam
from the vacuum chamber. It exploits a gap in the beam called abort gap (AG),
to ramp up the magnets and divert the beam towards beam dumps.
Imperfections in the accelerator may result in accumulation of particles inside
AG. This results in insufficient kicks, causing particles to deflect
towards the vacuum chamber and potentially leading to magnet quenching. This
why the AG needs to be continuously monitored by the abort gap monitor (AGM).

This paper reviews the upgrade of the current AGM system in the LHC since 2010,
focusing on system architecture, analog electronics chain, temperature
dependence, timing instabilities, and a comparison with the upgraded system.

The maximum beam energy in~LHC at flat-top distributed in 2808 bunches can
reach \SI{350}{MJ}, while having its average transverse size smaller than
\SI{1}{mm}[LHCreport]. Such energy density can cause damage to the machine. 
Inervention with conductive surface is enough to melt metallic surfaces and
quenching a superconductiv magnet. The Beam dump system safely removes beam
from the vacuum chamber. Its kicker magnets need \SI{3}{\micro\second} to ramp
up their magnetic field and diverge particles towards beam dumps. The particles
inside AG due to inperfections get insufficient kick and deflect towards the
vacuum chamber. At certain energy accumulated in AG, the magnet can quench.
Therefore continuous monitoring of the AG population is required. This is the
purpose of the AGM~[abortgapmonitor].\\ 
This paper reviews upgrade of the current AGM system installed in the LHC since
2010. It describes first general system architecture and analog electronics
chain of the current implementation. Discusses the temperature dependence,
timing instabilities and compares the current and upgraded system.

>>>>

\section{Introduction}
During the flat-top phase, the LHC ring stores up to 350 MJ of beam energy,
spread across 2808 bunches with an average beam transverse size under
\SI{1}{mm}. This high energy density can melt metallic surfaces and quench
superconducting magnets, posing a risk to the machine~\cite{LHC_report}. 
To safely extract the beam from the vacuum compartments, a series of kicker
magnets belonging to the beam dump system is used. These magnets take 3 us to
ramp up their magnetic field~\cite{beam_dump_system}. This defines the size of
an abort gap (AG) in the bunch train. Due to system imperfections, particles
populate this gap. Average AG population is in order of $10^{9}$ particles. The
population in a single bunch is four orders of magnitude higher in comparison.
When the beam dump is initiated, the particles in AG do not receive full
extraction force. That causes deflection towards the vacuum chamber. When a
certain energy accumulates in the AG, the magnet can quench. Therefore,
continuous monitoring of the AG population is necessary, which is the purpose
of the AGM~\cite{particles_in_ag}.\\
This paper reviews the upgrade of the current AGM system in the LHC since 2010,
focusing on system architecture, analog electronics chain, temperature
dependence, timing instabilities, and a comparison with the upgraded system.
